---
title: "Untitled"
author: "Aishwarya Kothari"
date: "3/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(lmerTest)
library(car)
library(zoo)
library(beanplot)
library(emmeans)
library(lme4)
```


######spikelet number per head######
#####CONTROL#####

####################################################
######Rep 1 ########################################
####################################################
```{r}
spike <- read_excel("harvesting rep 1.xlsx", sheet = 3)
head(spike)

spike$Chamber <- as.factor(spike$Chamber)
spike$Plant <- as.factor(spike$Plant)

spike$single <- paste(spike$Line, spike$BL, spike$HeatStress, spike$Plant, spike$Spike, sep = "_")
```

###simpler Vida
```{r}
head(spike)
vida <- spike[spike$Line =="Vida",]
vidaAgg<- aggregate(vida$Spike, by = list(vida$HeatStress, vida$BL, vida$Plant, vida$Spike), FUN= length)

par(mfrow = c(1,3))
par(mar = c(5,5,2,2))
boxplot(vidaAgg[vidaAgg$Group.2 == "C",5] ~ vidaAgg[vidaAgg$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 1")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
```

```{r}

leveneTest(vidaAgg[vidaAgg$Group.2 == "C",5] ~ vidaAgg[vidaAgg$Group.2 == "C",1])
wilcox.test(vidaAgg[vidaAgg$Group.2 == "C",5] ~ vidaAgg[vidaAgg$Group.2 == "C",1])
```

```{r}
hiline<-spike[spike$Line =="Hiline",]
hilAgg<- aggregate(hiline$Spike, by = list(hiline$HeatStress, hiline$BL, hiline$Plant, hiline$Spike), FUN= length)

par(mfrow = c(1,3))
par(mar = c(5,5,2,2))
boxplot(hilAgg[hilAgg$Group.2 == "C",5] ~ hilAgg[hilAgg$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 1")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
```

```{r}
leveneTest(hilAgg[hilAgg$Group.2 == "C",5] ~ hilAgg[hilAgg$Group.2 == "C",1])
wilcox.test(hilAgg[hilAgg$Group.2 == "C",5] ~ hilAgg[hilAgg$Group.2 == "C",1])
```

```{r}
mth<-spike[spike$Line =="MTH",]
mtAgg<- aggregate(mth$Spike, by = list(mth$HeatStress, mth$BL, mth$Plant, mth$Spike), FUN= length)

par(mfrow = c(1,3))
par(mar = c(5,5,2,2))
boxplot(mtAgg[mtAgg$Group.2 == "C",5] ~ mtAgg[hilAgg$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 1")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
```

```{r}
leveneTest(mtAgg[mtAgg$Group.2 == "C",5] ~ mtAgg[mtAgg$Group.2 == "C",1])
wilcox.test(mtAgg[mtAgg$Group.2 == "C",5] ~ mtAgg[mtAgg$Group.2 == "C",1])
```

####################################################
######Rep 2 ########################################
####################################################
```{r}
spike2 <- read_excel(path = "harvesting rep 2.xlsx", sheet = 2)
head(spike2)

spike2$Chamber <- as.factor(spike2$Chamber)
spike2$Plant <- as.factor(spike2$Plant)

spike2$single <- paste(spike2$Line, spike2$BL, spike2$HeatStress, spike2$Plant, spike2$Spike, sep = "_")
```

###simpler Vida
```{r}
vida2 <- spike2[spike2$Line =="Vida",]
vidaAgg2<- aggregate(vida2$Spike, by = list(vida2$HeatStress, vida2$BL, vida2$Plant, vida2$Spike), FUN= length)
par(mar = c(5,5,2,2))

boxplot(vidaAgg2[vidaAgg2$Group.2 == "C",5] ~ vidaAgg2[vidaAgg$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 2")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
```

```{r}
leveneTest(vidaAgg2[vidaAgg2$Group.2 == "C",5] ~ vidaAgg2[vidaAgg2$Group.2 == "C",1])
wilcox.test(vidaAgg2[vidaAgg2$Group.2 == "C",5] ~ vidaAgg2[vidaAgg2$Group.2 == "C",1])
```

```{r}
hiline2<-spike2[spike2$Line =="Hiline",]
hilAgg2<- aggregate(hiline2$Spike, by = list(hiline2$HeatStress, hiline2$BL, hiline2$Plant, hiline2$Spike), FUN= length)

par(mfrow = c(1,3))
par(mar = c(5,5,2,2))
boxplot(hilAgg2[hilAgg2$Group.2 == "C",5] ~ hilAgg2[hilAgg2$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 1")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
```

```{r}
leveneTest(hilAgg2[hilAgg2$Group.2 == "C",5] ~ hilAgg2[hilAgg2$Group.2 == "C",1])
wilcox.test(hilAgg2[hilAgg2$Group.2 == "C",5] ~ hilAgg2[hilAgg2$Group.2 == "C",1])
```

```{r}
mth2<-spike2[spike2$Line =="MTH",]
mtAgg2<- aggregate(mth2$Spike, by = list(mth2$HeatStress, mth2$BL, mth2$Plant, mth2$Spike), FUN= length)

par(mfrow = c(1,3))
par(mar = c(5,5,2,2))
boxplot(mtAgg2[mtAgg2$Group.2 == "C",5] ~ mtAgg2[hilAgg2$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 1")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
```

```{r}
leveneTest(mtAgg2[mtAgg2$Group.2 == "C",5] ~ mtAgg2[mtAgg2$Group.2 == "C",1])
wilcox.test(mtAgg2[mtAgg2$Group.2 == "C",5] ~ mtAgg2[mtAgg2$Group.2 == "C",1])
```


####################################################
######Rep 3 ########################################
####################################################
```{r}
spike3 <- read_excel(path = "harvesting rep 3.xlsx", sheet = 2)


spike3$Chamber <- as.factor(spike3$Chamber)
spike3$Plant <- as.factor(spike3$Plant)

spike3$single <- paste(spike3$Line, spike3$BL, spike3$HeatStress, spike3$Plant, spike3$Spike, sep = "_")
```

###simpler Vida
```{r}
vida3 <- spike3[spike3$Line =="Vida",]
vidaAgg3<- aggregate(vida3$Spike, by = list(vida3$HeatStress, vida3$BL, vida3$Plant, vida3$Spike), FUN= length)
par(mar = c(5,5,2,2))

boxplot(vidaAgg3[vidaAgg3$Group.2 == "C",5] ~ vidaAgg3[vidaAgg3$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), , main = "Rep 3")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
```

```{r}
leveneTest(vidaAgg3[vidaAgg3$Group.2 == "C",5] ~ vidaAgg3[vidaAgg3$Group.2 == "C",1])
wilcox.test(vidaAgg3[vidaAgg3$Group.2 == "C",5] ~ vidaAgg3[vidaAgg3$Group.2 == "C",1])
```

```{r}
hiline3<-spike3[spike3$Line =="Hiline",]
hilAgg3<- aggregate(hiline3$Spike, by = list(hiline3$HeatStress, hiline3$BL, hiline3$Plant, hiline3$Spike), FUN= length)

par(mfrow = c(1,3))
par(mar = c(5,5,2,2))
boxplot(hilAgg3[hilAgg3$Group.2 == "C",5] ~ hilAgg3[hilAgg3$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 1")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
```

```{r}
leveneTest(hilAgg3[hilAgg3$Group.2 == "C",5] ~ hilAgg3[hilAgg3$Group.2 == "C",1])
wilcox.test(hilAgg3[hilAgg3$Group.2 == "C",5] ~ hilAgg3[hilAgg3$Group.2 == "C",1])
```

```{r}
mth3<-spike3[spike3$Line =="MTH",]
mtAgg3<- aggregate(mth3$Spike, by = list(mth3$HeatStress, mth3$BL, mth3$Plant, mth3$Spike), FUN= length)

par(mfrow = c(1,3))
par(mar = c(5,5,2,2))
boxplot(mtAgg3[mtAgg3$Group.2 == "C",5] ~ mtAgg3[hilAgg3$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 1")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
```

```{r}
leveneTest(mtAgg3[mtAgg3$Group.2 == "C",5] ~ mtAgg3[mtAgg3$Group.2 == "C",1])
wilcox.test(mtAgg3[mtAgg3$Group.2 == "C",5] ~ mtAgg3[mtAgg3$Group.2 == "C",1])
```

##########

```{r}
par(mfrow = c(1,3))
par(mar = c(5,5,2,2))
boxplot(hilAgg[hilAgg$Group.2 == "C",5] ~ hilAgg[hilAgg$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 1")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
boxplot(hilAgg2[hilAgg2$Group.2 == "C",5] ~ hilAgg2[hilAgg2$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 1")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
boxplot(hilAgg3[hilAgg3$Group.2 == "C",5] ~ hilAgg3[hilAgg3$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 1")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
```

```{r}
par(mfrow = c(1,3))
par(mar = c(5,5,2,2))
boxplot(mtAgg[mtAgg$Group.2 == "C",5] ~ mtAgg[mtAgg$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 1")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
boxplot(mtAgg2[mtAgg2$Group.2 == "C",5] ~ mtAgg2[mtAgg2$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 2")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
boxplot(mtAgg3[mtAgg3$Group.2 == "C",5] ~ mtAgg3[mtAgg3$Group.2 == "C",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 3")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
```





#####SEED TREATMENT#####

####################################################
######Rep 1 ########################################
####################################################
```{r}
spike <- read_excel(path = "/Users/jenniferlachowiec/Dropbox/Montana State/projects/Aish/harvesting rep 1.xlsx", sheet = 3)
head(spike)

spike$Chamber <- as.factor(spike$Chamber)
spike$Plant <- as.factor(spike$Plant)

spike$single <- paste(spike$Line, spike$BL, spike$HeatStress, spike$Plant, spike$Spike, sep = "_")
```

###simpler Vida
```{r}
head(spike)
vida <- spike[spike$Line =="Vida",]
vidaAgg<- aggregate(vida$Spike, by = list(vida$HeatStress, vida$BL, vida$Plant, vida$Spike), FUN= length)

par(mfrow = c(1,3))
par(mar = c(5,5,2,2))
boxplot(vidaAgg[vidaAgg$Group.2 == "S",5] ~ vidaAgg[vidaAgg$Group.2 == "S",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 1")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
```

```{r}
leveneTest(vidaAgg[vidaAgg$Group.2 == "S",5] ~ vidaAgg[vidaAgg$Group.2 == "S",1])
wilcox.test(vidaAgg[vidaAgg$Group.2 == "S",5] ~ vidaAgg[vidaAgg$Group.2 == "S",1])
```

####################################################
######Rep 2 ########################################
####################################################
```{r}
spike <- read_excel(path = "/Users/jenniferlachowiec/Dropbox/Montana State/projects/Aish/harvesting rep 2.xlsx", sheet = 2)
head(spike)

spike$Chamber <- as.factor(spike$Chamber)
spike$Plant <- as.factor(spike$Plant)

spike$single <- paste(spike$Line, spike$BL, spike$HeatStress, spike$Plant, spike$Spike, sep = "_")
```

###simpler Vida
head(spike)
vida <- spike[spike$Line =="Vida",]
vidaAgg<- aggregate(vida$Spike, by = list(vida$HeatStress, vida$BL, vida$Plant, vida$Spike), FUN= length)
par(mar = c(5,5,2,2))

boxplot(vidaAgg[vidaAgg$Group.2 == "S",5] ~ vidaAgg[vidaAgg$Group.2 == "S",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 2")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)



leveneTest(vidaAgg[vidaAgg$Group.2 == "S",5] ~ vidaAgg[vidaAgg$Group.2 == "S",1])
wilcox.test(vidaAgg[vidaAgg$Group.2 == "S",5] ~ vidaAgg[vidaAgg$Group.2 == "S",1])




####################################################
######Rep 3 ########################################
####################################################

spike <- read_excel(path = "/Users/jenniferlachowiec/Dropbox/Montana State/projects/Aish/harvesting rep 3.xlsx", sheet = 2)
head(spike)

spike$Chamber <- as.factor(spike$Chamber)
spike$Plant <- as.factor(spike$Plant)

spike$single <- paste(spike$Line, spike$BL, spike$HeatStress, spike$Plant, spike$Spike, sep = "_")


###simpler Vida
head(spike)
vida <- spike[spike$Line =="Vida",]
vidaAgg<- aggregate(vida$Spike, by = list(vida$HeatStress, vida$BL, vida$Plant, vida$Spike), FUN= length)
par(mar = c(5,5,2,2))

boxplot(vidaAgg[vidaAgg$Group.2 == "S",5] ~ vidaAgg[vidaAgg$Group.2 == "S",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), , main = "Rep 3")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)



leveneTest(vidaAgg[vidaAgg$Group.2 == "S",5] ~ vidaAgg[vidaAgg$Group.2 == "S",1])
wilcox.test(vidaAgg[vidaAgg$Group.2 == "S",5] ~ vidaAgg[vidaAgg$Group.2 == "S",1])

```{r}
par(mfrow = c(1,3))
par(mar = c(5,5,2,2))
boxplot(mtAgg[mtAgg$Group.2 == "S",5] ~ mtAgg[mtAgg$Group.2 == "S",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 1")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
boxplot(mtAgg2[mtAgg2$Group.2 == "S",5] ~ mtAgg2[mtAgg2$Group.2 == "S",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 2")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
boxplot(mtAgg3[mtAgg3$Group.2 == "S",5] ~ mtAgg3[mtAgg3$Group.2 == "S",1], xlab = "heat stress",
        ylab = "spikelet number per head", col = c("blue", "orange"), 
        cex.lab=2, names.arg = 2, las = 2, xaxt="n", yaxt="n",
        ylim = c(0,25), main = "Rep 3")
axis(1, at=c(1,2), labels=c("22 degrees", "29 degrees"), cex.axis=1.7)
axis(2, at=c(0:25), labels=0:25, cex.axis=1, las = 2)
```

####################################################
##############################################
####################################################

#####fertility--grain per floret######
####fertility rep1####
```{r}
spike <- read_excel(path = "/Users/jenniferlachowiec/Dropbox/Montana State/projects/Aish/harvesting rep 1.xlsx", sheet = 3)
head(spike)

spike$Chamber <- as.factor(spike$Chamber)
spike$Plant <- as.factor(spike$Plant)

spike$single <- paste(spike$Line, spike$BL, spike$HeatStress, spike$Plant, spike$Spike, sep = "_")
```

```{r}
spike$fert <- spike$GrainNo./spike$Floret
vidaf <- spike[spike$Line =="Vida",]
vf<- aggregate(vidaf$fert, by = list(vidaf$HeatStress, vidaf$BL, vidaf$Plant, vidaf$Spike), FUN= mean)
names(vf) <- c("Heat", "BL", "Plant", "Spike", "Fertility")
vf$Plant <- as.factor(vf$Plant)
vf$Spike <- as.factor(vf$Spike)

par(mfrow = c(1,1))
boxplot(vf$Fertility ~ vf$Heat + vf$BL, col = c("blue", "orange"))
```


```{r}
mod0 <- lmer(log(Fertility+0.01) ~ BL * Heat + (1|Spike/Plant), data = vidaAgg )
plot(mod0)
Anova(mod0)
eem <- emmeans(mod0, c("Heat", "BL"))
plot(eem)
```

####fertility rep2####
```{r}
spike <- read_excel(path = "/Users/jenniferlachowiec/Dropbox/Montana State/projects/Aish/harvesting rep 2.xlsx", sheet = 2)
head(spike)

spike$Chamber <- as.factor(spike$Chamber)
spike$Plant <- as.factor(spike$Plant)

spike$single <- paste(spike$Line, spike$BL, spike$HeatStress, spike$Plant, spike$Spike, sep = "_")
```

```{r}
spike$fert <- spike$GrainNo./spike$Floret
vida <- spike[spike$Line =="Vida",]
vidaAgg<- aggregate(vida$fert, by = list(vida$HeatStress, vida$BL, vida$Plant, vida$Spike), FUN= mean)
head(vidaAgg)
names(vidaAgg) <- c("Heat", "BL", "Plant", "Spike", "Fertility")
vidaAgg$Plant <- as.factor(vidaAgg$Plant)
vidaAgg$Spike <- as.factor(vidaAgg$Spike)

par(mfrow = c(1,1))
boxplot(vidaAgg$Fertility ~ vidaAgg$Heat + vidaAgg$BL, col = c("blue", "orange"))
```

```{r}
mod0 <- lmer(log(Fertility+0.01) ~ BL * Heat + (1|Spike/Plant), data = vidaAgg )
plot(mod0)
Anova(mod0)
eem <- emmeans(mod0, c("Heat", "BL"))
plot(eem)
```

####fertility rep3####
```{r}
spike <- read_excel(path = "/Users/jenniferlachowiec/Dropbox/Montana State/projects/Aish/harvesting rep 3.xlsx", sheet = 2)
head(spike)

spike$Chamber <- as.factor(spike$Chamber)
spike$Plant <- as.factor(spike$Plant)

spike$single <- paste(spike$Line, spike$BL, spike$HeatStress, spike$Plant, spike$Spike, sep = "_")
```

```{r}
spike$fert <- spike$GrainNo./spike$Floret
vida <- spike[spike$Line =="Vida",]
vidaAgg<- aggregate(vida$fert, by = list(vida$HeatStress, vida$BL, vida$Plant, vida$Spike), FUN= mean)
head(vidaAgg)
names(vidaAgg) <- c("Heat", "BL", "Plant", "Spike", "Fertility")
vidaAgg$Plant <- as.factor(vidaAgg$Plant)
vidaAgg$Spike <- as.factor(vidaAgg$Spike)

par(mfrow = c(1,1))
boxplot(vidaAgg$Fertility ~ vidaAgg$Heat + vidaAgg$BL, col = c("blue", "orange"))
```

```{r}
mod0 <- lmer(log(Fertility+0.01) ~ BL * Heat + (1|Spike/Plant), data = vidaAgg )
plot(mod0)
Anova(mod0)
eem <- emmeans(mod0, c("Heat", "BL"))
plot(eem)
```
