---
title: "Untitled"
author: "Aishwarya Kothari"
date: "3/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
suppressMessages(library(readxl))
suppressMessages(library(car))
suppressMessages(library(mosaic))
suppressMessages(library(yarrr))
suppressMessages(library(lmerTest))
suppressMessages(library(emmeans))
suppressMessages(library(effects))
suppressMessages(library(ggplot2))
suppressMessages(library(Rmisc))
suppressMessages(library(multcompView))
suppressMessages(library(multcomp))

```


Plant height

```{r}
mwb1<-read_excel("combined reps.xlsx", sheet=1)

mwb1$Variety<-factor(mwb1$Variety)
mwb1$BL<-factor(mwb1$BL)
mwb1$HeatStress<-factor(mwb1$HeatStress)
mwb1$Rep<-factor(mwb1$Rep)
```



Pooling Vida only 
```{r}
vida <- mwb1[mwb1$Variety == "Vida",]
newdata1<-vida
```

```{r}
control <- mwb1[mwb1$Variety == "Vida"& mwb1$BL == "C",]
seed <- mwb1[mwb1$Variety == "Vida"& mwb1$BL == "S",]
newdata<-rbind(control,seed)

newdata<-newdata[-c(39),]
```


```{r}
m1<-lmer(PlantHeight~BL*HeatStress+(1|Rep)+(1|Chamber), data=newdata)
m2<-lmer(PlantHeight~BL+HeatStress+(1|Rep)+(1|Chamber), data=newdata)
Anova(m1, test.statistic = "F")
Anova(m2, test.statistic = "F")
summary(m1)
```



```{r}
newdata$treat<-with(newdata, interaction(BL,HeatStress))

model<-lmer(PlantHeight~treat+(1|Rep)+(1|Chamber), data=newdata)
Anova(model, test.statistic = "F")
```

```{r}
trt<-glht(model,linfct=mcp(treat="Tukey"))
summary(trt)
confint(trt)
```

```{r}
cld(trt)
```



```{r}
trts<-glht(m1, linfct=mcp("BL"="Tukey","HeatStress"="Tukey"))
summary(trts)
confint(trts)
```







Spike length

vida

```{r}
mwb3<-read_excel("combined reps.xlsx", sheet=3)

mwb3$Line<-factor(mwb3$Line)
mwb3$BL<-factor(mwb3$BL)
mwb3$HeatStress<-factor(mwb3$HeatStress)
mwb3$Rep<-factor(mwb3$Rep)
```




```{r}
vidaSL<-mwb3[mwb3$Line == "Vida",]
nd<-vidaSL
controlv2 <- mwb3[mwb3$Line == "Vida"& mwb3$BL == "C",]
seedv2 <- mwb3[mwb3$Line == "Vida"& mwb3$BL == "S",]
newdata7<-rbind(controlv2,seedv2)
```


```{r}
m3<-lmer(SpikeLength ~ HeatStress * BL+(1|Rep)+(1|Chamber), data=newdata7)
Anova(m3, test.statistic = "F")
m4<-lmer(SpikeLength ~ HeatStress + BL+(1|Rep)+(1|Chamber), data=newdata7)
Anova(m4, test.statistic = "F")
#summary(m9)
```


```{r}
trt1<-glht(m4, linfct=mcp("BL"="Tukey","HeatStress"="Tukey"))
summary(trt1)
confint(trt1)
```


```{r}
d<-emmeans(m18, c("BL", "HeatStress"))
emmip(m18,BL~HeatStress, CIs=TRUE)
emmip(m18,BL~HeatStress)
plot(d, comparison=T)
```

```{r}
newdata7$treat<-with(newdata7, interaction(BL,HeatStress))

model2<-lmer(SpikeLength~treat+(1|Rep)+(1|Chamber), data=newdata7)

trt2<-glht(model2,linfct=mcp(treat="Tukey"))
summary(trt2)
confint(trt2)
```






Grain Number per spike

```{r}
rep2<-read_excel("harvesting rep 2.xlsx", sheet=2)
rep1<-read_excel("harvesting rep 1.xlsx", sheet=3)
rep3<-read_excel("harvesting rep 3.xlsx", sheet=2)

```



```{r}
gN1 <- aggregate(rep1$GrainNo., by = list(rep1$Rep, rep1$Line,rep1$BL,rep1$Chamber,rep1$HeatStress, rep1$Plant,rep1$Spike), FUN = sum)
gN2 <- aggregate(rep2$GrainNo., by = list(rep2$Rep, rep2$Line,rep2$BL,rep2$Chamber,rep2$HeatStress, rep2$Plant,rep2$Spike), FUN=sum)
gN3 <- aggregate(rep3$GrainNo., by = list(rep3$Rep, rep3$Line,rep3$BL,rep3$Chamber,rep3$HeatStress, rep3$Plant,rep3$Spike), FUN = sum)

```




```{r}

grainNo1<-data.frame(gN1)
grainNo2<-data.frame(gN2)
grainNo3<-data.frame(gN3)



newdata8<-rbind(grainNo1,grainNo2, grainNo3)

```

write.csv(grainNo1,'C:/Users/r31j968/OneDrive - Montana State University - Bozeman/Documents/R analysis/grainNo1.csv', row.names = TRUE)
write.csv(grainNo2,'C:/Users/r31j968/OneDrive - Montana State University - Bozeman/Documents/R analysis/grainNo2.csv', row.names = TRUE)
write.csv(grainNo3,'C:/Users/r31j968/OneDrive - Montana State University - Bozeman/Documents/R analysis/grainNo3.csv', row.names = TRUE)


```{r}
names(newdata8)[names(newdata8) == "Group.1"] <- "Rep"
names(newdata8)[names(newdata8) == "Group.2"] <- "Line"
names(newdata8)[names(newdata8) == "Group.3"] <- "BL"
names(newdata8)[names(newdata8) == "Group.4"] <- "Chamber"
names(newdata8)[names(newdata8) == "Group.5"] <- "HS"
names(newdata8)[names(newdata8) == "Group.6"] <- "Plant"
names(newdata8)[names(newdata8) == "Group.7"] <- "Spike"
names(newdata8)[names(newdata8) == "x"] <- "GrainNo"
```


```{r}
newdata8$Line<-factor(newdata8$Line)
newdata8$BL<-factor(newdata8$BL)
newdata8$HS<-factor(newdata8$HS)
newdata8$Rep<-factor(newdata8$Rep)
```


```{r}
vidaGN <- newdata8[newdata8$Line == "Vida",]
hilGN <- newdata8[newdata8$Line == "Hiline",]
mthGN <- newdata8[newdata8$Line == "MTH",]
nd6<-vidaGN
nd7<-hilGN
nd8<-mthGN
```

```{r}
controlv3 <- newdata8[newdata8$Line == "Vida"& newdata8$BL == "C",]
seedv3 <- newdata8[newdata8$Line == "Vida"& newdata8$BL == "S",]
newdata2<-rbind(controlv3,seedv3)
```


```{r}
m5<-lmer(GrainNo ~ HS * BL+(1|Rep)+(1|Chamber), data=newdata2)
Anova(m5, test.statistic = "F")
m6<-lmer(GrainNo ~ HS + BL+(1|Rep)+(1|Chamber), data=newdata2)
Anova(m6, test.statistic = "F")
#summary(m13)
```

```{r}
trt3<-glht(m5, linfct=mcp("BL"="Tukey","HS"="Tukey"))
summary(trt3)
confint(trt3)
```

```{r}
newdata2$treat<-with(newdata2, interaction(BL,HS))

model5<-lmer(GrainNo~treat+(1|Rep)+(1|Chamber), data=newdata2)

trt4<-glht(model5,linfct=mcp(treat="Tukey"))
summary(trt4)
confint(trt4)
```



Grain weight
```{r}
SW<-newdata[!newdata$Rep=="3",]
SW$SeedWeight <- as.numeric(SW$SeedWeight)
```

```{r}
m16<-lmer(SeedWeight~BL*HeatStress+(1|Rep)+(1|Chamber), data=SW)
Anova(m16, test.statistic = "F")
summary(m16)
```
No sig difference

```{r}
m17<-lmer(SeedWeight~BL+HeatStress+(1|Rep)+(1|Chamber), data=SW)
Anova(m17, test.statistic = "F")
summary(m17)
```
No sig difference

```{r}
emmeans(m16,c("BL","HeatStress"))

emmip(m16,BL~HeatStress, CIs=TRUE)

emmeans(m17,c("BL","HeatStress"))

emmip(m17,BL~HeatStress, CIs=TRUE)
```


1000 grain weight

```{r}
thGW<-read_excel("1000 grain weight.xlsx", sheet=1)
```


```{r}
m23<-lmer(tGW~BL*HS+(1|Rep), data=thGW)
Anova(m23, test.statistic = "F")
summary(m23)
```

```{r}
m24<-lmer(tGW~BL+HS+(1|Rep), data=thGW)
Anova(m24, test.statistic = "F")
summary(m24)
```

```{r, fig.width=11}
intplotarray( tGW~BL*HS, data=thGW)
```

```{r}
pirateplot(tGW~BL+HS, data=thGW, inf.method = "ci")
```

```{r}
boxplot(tGW~BL+HS, data=thGW)

```

```{r}
vidaGW <- thGW[thGW$Line == "Vida",]
hilGW <- thGW[thGW$Line == "Hiline",]
mthGW <- thGW[thGW$Line == "MTH",]
nd1<-vidaGW
nd2<-hilGW
nd3<-mthGW
```


```{r}
pirateplot(tGW~BL+HS, data=nd1, inf.method = "ci")
pirateplot(tGW~BL+HS, data=nd2, inf.method = "ci")
pirateplot(tGW~BL+HS, data=nd3, inf.method = "ci")

```



```{r, fig.width=11}
intplotarray( tGW~BL*HS, data=nd1)
intplotarray( tGW~BL*HS, data=nd2)
intplotarray( tGW~BL*HS, data=nd3)
```

```{r}
m30<-lmer(tGW~BL*HS+(1|Rep), data=nd1)
Anova(m30, test.statistic = "F")
summary(m30)
```

```{r}
j<-emmeans(m30, c("BL", "HS"))
plot(j, comparison=T)
```

```{r}
nd1$treat<-with(nd1, interaction(BL,HS))

model8<-lmer(tGW~treat+(1|Rep), data=nd1)

trt8<-glht(model8,linfct=mcp(treat="Tukey"))
summary(trt8)
```

```{r}
m31<-lmer(tGW~BL+HS+(1|Rep), data=nd2)
Anova(m31, test.statistic = "F")
summary(m31)
```

```{r}
k<-emmeans(m31, c("BL", "HS"))
plot(k, comparison=T)
```

```{r}
nd2$treat<-with(nd2, interaction(BL,HS))

model9<-lmer(tGW~treat+(1|Rep), data=nd2)

trt9<-glht(model9,linfct=mcp(treat="Tukey"))
summary(trt9)
```

```{r}
m32<-lmer(tGW~BL+HS+(1|Rep), data=nd3)
Anova(m32, test.statistic = "F")
summary(m32)
```

```{r}
l<-emmeans(m32, c("BL", "HS"))
plot(l, comparison=T)
```

```{r}
nd3$treat<-with(nd3, interaction(BL,HS))

model10<-lmer(tGW~treat+(1|Rep), data=nd3)

trt10<-glht(model10,linfct=mcp(treat="Tukey"))
summary(trt10)
```

```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("limma")
library(limma)
```


```{r}
mol<-read_excel("mol data.xlsx", sheet=2)
mol$Gene<-factor(mol$Gene)

```

```{r}
SK2 <- mol[mol$Gene == "SK2",]
SERK1 <- mol[mol$Gene == "SERK1",]
BZR2 <- mol[mol$Gene == "BZR2",]
CPD <- mol[mol$Gene == "CPD",]
BRI1 <- mol[mol$Gene == "BRI1",]

```

```{r}
wilcox.test(NH-C,NH-S, data=mol)
wilcox.test(SK2$H-C~SK2$H-S)
wilcox.test(SK2$NH-C~SK2$H-C)
wilcox.test(SK2$NH-S~SK2$H-S)
```

```{r}
wilcox.test(BZR2$NH-C~BZR2$NH-S)
wilcox.test(BZR2$H-C~BZR2$H-S)
wilcox.test(BZR2$NH-C~BZR2$H-C)
wilcox.test(BZR2$NH-S~BZR2$H-S)
```

```{r}
wilcox.test(SERK1$NH-C~SERK1$NH-S)
wilcox.test(SERK1$H-C~SERK1$H-S)
wilcox.test(SERK1$NH-C~SERK1$H-C)
wilcox.test(SERK1$NH-S~SERK1$H-S)
```

```{r}
wilcox.test(CPD$NH-C~CPD$NH-S)
wilcox.test(CPD$H-C~CPD$H-S)
wilcox.test(CPD$NH-C~CPD$H-C)
wilcox.test(CPD$NH-S~CPD$H-S)
```

```{r}
wilcox.test(BRI1$NH-C~BRI1$NH-S)
wilcox.test(BRI1$H-C~BRI1$H-S)
wilcox.test(BRI1$NH-C~BRI1$H-C)
wilcox.test(BRI1$NH-S~BRI1$H-S)
```