---
title: "all reps combined"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
suppressMessages(library(readxl))
suppressMessages(library(car))
suppressMessages(library(mosaic))
suppressMessages(library(yarrr))
suppressMessages(library(lmerTest))
suppressMessages(library(emmeans))
suppressMessages(library(effects))
suppressMessages(library(ggplot2))
suppressMessages(library(Rmisc))
suppressMessages(library(multcomp))
```

```{r}
mwb1<-read_excel("combined reps.xlsx", sheet=1)

mwb1$Variety<-factor(mwb1$Variety)
mwb1$BL<-factor(mwb1$BL)
mwb1$HeatStress<-factor(mwb1$HeatStress)
mwb1$Rep<-factor(mwb1$Rep)
```

```{r}
colnames(mwb1)
names(mwb1)[names(mwb1) == "HeatStress"] <- "Stress"
```

Change HeatStress to Stress everywhere hence forward. 

```{r, fig.width=11}
pirateplot(PlantHeight~Variety+BL, data=mwb1, inf.method="ci",cex.names=0.8)
```

```{r}
pirateplot(PlantHeight ~ Variety + Stress, inf.method = "ci", cex.names = 0.8, ylab = "Mean Plant Height (cm)", data=mwb1)
```


Graph of plant height vs all varieties and treatments, mixing both heat stress and control. 

```{r}
pirateplot(PlantHeight~Variety +Rep, data=mwb1, inf.method="ci",cex.names=0.8)
```



Pooling Vida only 
```{r}
vida <- mwb1[mwb1$Variety == "Vida",]
newdata1<-vida
```

```{r}
pirateplot(PlantHeight ~ BL + Stress, inf.method = "ci", ylab="Mean Plant Height (cm)", data=newdata1)
```


```{r}
pirateplot(vida$PlantHeight ~ vida$BL + vida$Stress + vida$Rep , data=mwb1)
```

In all reps, heat stress overall reduced plant height. 
In rep 1: D,F,H had taller plants than C under heat stress. In control plants (no HS), BL did not seem to have a positive effect on plant height; C treatment plants were taller. 
In rep 2: S had taller plants than C in both HS and no HS. In no HS: F and H had taller plants than C. In HS: all BL treatments had taller plants than C
In rep 3: D,S had taller plants than C in HS. 

```{r}
pirateplot(vida$PlantHeight ~ vida$BL +  vida$Rep,inf.method="ci" , data=mwb1)
```

```{r}
pirateplot(vida$PlantHeight ~ vida$Stress + vida$Rep,inf.method="ci" , data=mwb1)
```

In all 3 reps, HS reduced plant height. But, reps 2 and 3 had less reduction in height compared to rep 1.

```{r}
pirateplot(vida$PlantHeight ~ vida$Rep,inf.method="ci" , data=mwb1)
```

```{r}
pirateplot(vida$TillerNumber ~ vida$BL + vida$Stress + vida$Rep , data=mwb1)
```

Can't say a lot about tiller number, it is inconclusive. 

```{r}
pirateplot(vida$TillerNumber ~ vida$BL +  vida$Rep,inf.method="ci" , data=mwb1)
```

```{r}
pirateplot(vida$TillerNumber ~ vida$Stress + vida$Rep,inf.method="ci" , data=mwb1)
```

HS reduced tiller number in reps 1 and 3. 

```{r}
pirateplot(vida$TillerNumber ~ vida$Rep,inf.method="ci" , data=mwb1)
```


```{r, fig.width=9, fig.align='center', fig.height=6}
pirateplot(PlantHeight ~ BL + Stress+Rep,xlab="Treatment", ylab="Plant height",inf.method="ci",data=mwb1)
```

```{r}
pirateplot(PlantHeight ~ Rep, ylab="Plant height",inf.method="ci",data=mwb1)
```

```{r}
pirateplot(PlantHeight ~ Stress+ Variety+Rep , data=mwb1,inf.method="ci",ylab="plant height")
```

```{r}
pirateplot(PlantHeight ~ BL+ Variety+Rep , data=mwb1,ylab="plant height")

```



```{r}
pirateplot(TillerNumber ~ BL + Stress+Rep,data=mwb1,inf.method="ci")
pirateplot(TillerNumber ~ Variety + Stress+Rep,data=mwb1,inf.method="ci", cex.names = 0.7)

```

```{r,fig.width=11}
pirateplot(TillerNumber ~ Variety + Rep + BL, data=mwb1, cex.names=0.8,cex.lab = 0.8)
```

```{r}
m0<-lmer(PlantHeight~BL*Stress+(1|Rep)+(1|Chamber), data=newdata1)
Anova(m0)
summary(m0)
```


```{r}
control <- mwb1[mwb1$Variety == "Vida"& mwb1$BL == "C",]
seed <- mwb1[mwb1$Variety == "Vida"& mwb1$BL == "S",]
newdata<-rbind(control,seed)

##newdata<-newdata[-c(39),]
```

```{r}
pirateplot(PlantHeight~BL+Stress+Rep, data=newdata,cex.names=0.8, ylim=c(30,80))
```

```{r}
pairs(~PlantHeight+Stress+BL, data=newdata)
```


```{r}
boxplot(PlantHeight~BL+Stress+Rep, data=newdata,cex.names=0.8)

```

```{r}
pirateplot(TillerNumber~BL+Stress+Rep, data=newdata,cex.names=0.8)

```



```{r}
m1<-lmer(PlantHeight~BL*Stress+(1|Rep), data=newdata1)
Anova(m1)
summary(m1)
```

Only rep as random effect.  C, D Heat stress (HS), D*HS are significantly different 



```{r}
suppressMessages(library(xtable))
```


```{r}
m2<-lmer(PlantHeight~BL*Stress+(1|Rep)+(1|Chamber), data=newdata1)
Anova(m2, test.statistic = "F")
summary(m2)



##m12<-lmer(PlantHeight~BL*Stress+(1|Chamber)+(1|Rep), data=newdata1)
##m13<-lmer(PlantHeight~BL*Stress+(1|Chamber/Rep), data=newdata1)

```

model2<-summary(m2)$coefficients
out1<-xtable(model2)
out1
capture.output(model2, file="PH.xlxs")


capture.output(summary(m2),file="test.doc")

```{r}
newdata1$treat<-with(newdata1, interaction(BL,Stress))
```

```{r}
model<-lmer(PlantHeight~treat+(1|Rep)+(1|Chamber), data=newdata1)
Anova(model)
```

```{r}
trt<-glht(model,linfct=mcp(treat="Tukey"))
summary(trt)
confint(trt)
```

```{r}
cld(trt)
```


```{r}
emmeans(m2, pairwise~BL|Stress)
```


```{r}
a<-emmeans(m2, c("BL", "Stress"))
emmip(m2,BL~Stress, CIs=TRUE)
emmip(m2,BL~Stress)
plot(a, comparison=T)

```

```{r}
suppressMessages(library(multcompView))
cld(a)
```



```{r}
suppressMessages(library(multcomp))
trts<-glht(m2, linfct=mcp("BL"="Tukey","Stress"="Tukey"))
summary(trts)
confint(trts)
```


It doesn't matter which way I do random effects, it gives me the same result. 

Both rep and chamber as random effects. C, D*HS are significantly different. Maybe S shows little difference (p-value=0.5)




```{r}
m3<-lmer(PlantHeight~BL*Stress+(1|Rep)+(1|Chamber), data=newdata)
Anova(m3, test.statistic = "F")
summary(m3)
mean1<-emmeans(m3, c("BL","Stress"))
mean1
```
S, S*HS significantly different (after removing the outlier in Rep 2) 

```{r}
m<-emmeans(m3, c("BL", "Stress"))
emmip(m3,BL~Stress, CIs=TRUE)
emmip(m3,BL~Stress)
plot(m, comparison=T)
```



nd$treat<-with(nd, interaction(BL,Stress))

model2<-lmer(SpikeLength~treat+(1|Rep)+(1|Chamber), data=nd)

trt11<-glht(m3,linfct=mcp(treat="Tukey"))
summary(trt11)
confint(trt11)



calc_se<-summarySE(newdata, measurevar="PlantHeight", groupvars=c("BL","Stress"))
calc_se
pd <- position_dodge(0.1) # move them .05 to the left and right
ggplot(calc_se, aes(x=Stress, y=PlantHeight, group=BL))+
  geom_errorbar(aes(ymin=PlantHeight-sd, ymax=PlantHeight+sd),width=0.1, position=pd)+
  geom_line(aes(linetype=BL), position=pd)+
  geom_point(position=pd)



ggplot(tgc, aes(x=dose, y=len, colour=supp)) + 
    geom_errorbar(aes(ymin=len-se, ymax=len+se), width=.1) +
    geom_line() +
    geom_point()

```{r}
library(predictmeans)
residplot(m3, newwd=F)
residplot(m2,newwd=F)
```




```{r}

PHforplot<-data.frame(mean1)


#write.csv(PHforplot,'C:/Users/r31j968/OneDrive - Montana State University - Bozeman/Documents/R analysis/PHforplot.csv', row.names = TRUE)


```

```{r}
emmip(m3,BL~Stress, CIs=TRUE)
```

```{r, fig.width=11}
plot(mean1, comparison=T)
```


```{r, fig.width=11}
source("http://www.math.montana.edu/courses/s217/documents/intplotfunctions_v2.R")
intplotarray(PlantHeight~BL*Stress, data=newdata)
```


```{r, fig.width=11}
intplotarray(PlantHeight~BL*Stress, data=newdata1)

```

```{r, fig.width=11}
intplotarray(emmean~BL*Stress, data=PHforplot)

```

```{r}
interaction.plot(x.factor = PHforplot$'Stress', trace.factor = PHforplot$'BL', response = PHforplot$'emmean',  lwd = 5, fun = function(x) mean(x, na.rm = TRUE), xlab="heat stress", ylab="plant height")
```



```{r}
plot(allEffects(m3), multiline=T, grid=T, ci.style="bars")
```



```{r}
Anova(m3, test.statistic = "F")
anova(m3, type="II")
```
Can use either method, both give similar results. 

```{r}
m4<-lmer(PlantHeight~BL+Stress+(1|Rep)+(1|Chamber), data=newdata)
Anova(m4, test.statistic = "F")
summary(m4)
```

```{r}
anova(m4, m3)
```
So, there is some interaction between BL and heat stress, so keep the interaction term in the model. 





Hiline

```{r}
hiline <- mwb1[mwb1$Variety == "Hiline",]
Hil<-hiline

pirateplot(hiline$PlantHeight ~ hiline$BL + hiline$Stress + hiline$Rep , data=mwb1)
```

```{r}
pirateplot(PlantHeight~ BL + Stress, inf.method = "ci", ylab = "Mean Plant Height (cm)", data=Hil)
```


```{r}
pirateplot(hiline$PlantHeight ~ hiline$BL +  hiline$Rep,inf.method="ci" , data=mwb1)
```


```{r}
pirateplot(hiline$PlantHeight ~ hiline$Stress + hiline$Rep,inf.method="ci" , data=mwb1)
```


```{r}
pirateplot(hiline$PlantHeight ~ hiline$Rep,inf.method="ci" , data=mwb1)
```


```{r}
controlH <- mwb1[mwb1$Variety == "Hiline"& mwb1$BL == "C",]
seedH <- mwb1[mwb1$Variety == "Hiline"& mwb1$BL == "S",]
newdata2<-rbind(controlH,seedH)
```

```{r}
pirateplot(PlantHeight~BL+Stress+Rep, data=newdata2,cex.names=0.8, ylim=c(25,60))
```

```{r}
pirateplot(TillerNumber~BL+Stress+Rep, data=newdata2,cex.names=0.8)

```

```{r}
m19<-lmer(PlantHeight~BL*Stress+(1|Rep)+(1|Chamber), data=Hil)
Anova(m19, test.statistic = "F")
```

```{r}
m20<-lmer(PlantHeight~BL+Stress+(1|Rep)+(1|Chamber), data=Hil)
Anova(m20, test.statistic = "F")
summary(m20)
```

```{r, fig.width=11}
intplotarray(PlantHeight~BL*Stress, data=Hil)

```

```{r}
b<-emmeans(m20, c("BL", "Stress"))
emmip(m20,BL~Stress, CIs=TRUE)
emmip(m20,BL~Stress)
plot(b, comparison=T)
```

```{r}
Hil$treat<-with(Hil, interaction(BL,Stress))

model1<-lmer(PlantHeight~treat+(1|Rep)+(1|Chamber), data=Hil)

trt<-glht(model1,linfct=mcp(treat="Tukey"))
summary(trt)
confint(trt)
```

```{r}
m5<-lmer(PlantHeight~BL+Stress+(1|Rep)+(1|Chamber), data=newdata2)
Anova(m5, test.statistic = "F")
summary(m5)
```


```{r}
m6<-lmer(PlantHeight~BL*Stress+(1|Rep)+(1|Chamber), data=newdata2)
Anova(m6, test.statistic = "F")
summary(m6)
```

```{r}
mean3<-emmeans(m6,c("BL","Stress"))
PHforplot2<-data.frame(mean3)


#write.csv(PHforplot2,'C:/Users/r31j968/OneDrive - Montana State University - Bozeman/Documents/R analysis/PHforplot2.csv', row.names = TRUE)

emmip(m6,BL~Stress, CIs=TRUE)
```



MTH


```{r}
mth <- mwb1[mwb1$Variety == "MTH",]
MT<-mth

pirateplot(mth$PlantHeight ~ mth$BL + mth$Stress + mth$Rep , data=mwb1)
```

```{r}
pirateplot(PlantHeight~BL+Stress, inf.method = "ci", ylab="Mean Plant Height (cm)", data=MT)
```


```{r}
pirateplot(mth$PlantHeight ~ mth$BL +  mth$Rep,inf.method="ci" , data=mwb1)
```


```{r}
pirateplot(mth$PlantHeight ~ mth$Stress + mth$Rep,inf.method="ci" , data=mwb1)
```


```{r}
pirateplot(mth$PlantHeight ~ mth$Rep,inf.method="ci" , data=mwb1)
```


```{r}
controlM <- mwb1[mwb1$Variety == "MTH"& mwb1$BL == "C",]
seedM <- mwb1[mwb1$Variety == "MTH"& mwb1$BL == "S",]
newdata4<-rbind(controlM,seedM)
```

```{r}
pirateplot(PlantHeight~BL+Stress+Rep, data=newdata4,cex.names=0.8, ylim=c(30,75))
```

```{r}
pirateplot(TillerNumber~BL+Stress+Rep, data=newdata4,cex.names=0.8)

```

```{r}
m21<-lmer(PlantHeight~BL+Stress+(1|Rep)+(1|Chamber), data=MT)
Anova(m21, test.statistic = "F")
summary(m21)
```

```{r, fig.width=11}
intplotarray(PlantHeight~BL*Stress, data=MT)

```

```{r}
c<-emmeans(m21, c("BL", "Stress"))
emmip(m21,BL~Stress, CIs=TRUE)
emmip(m21,BL~Stress)
plot(c, comparison=T)
```

```{r}
MT$treat<-with(MT, interaction(BL,Stress))

model1<-lmer(PlantHeight~treat+(1|Rep)+(1|Chamber), data=MT)

trt<-glht(model1,linfct=mcp(treat="Tukey"))
summary(trt)
confint(trt)
```

```{r}
m7<-lmer(PlantHeight~BL+Stress+(1|Rep)+(1|Chamber), data=newdata4)
Anova(m7, test.statistic = "F")
summary(m7)
```


```{r}
m8<-lmer(PlantHeight~BL*Stress+(1|Rep)+(1|Chamber), data=newdata4)
Anova(m8, test.statistic = "F")
summary(m8)
```


```{r}
mean4<-emmeans(m7,c("BL","Stress"))
PHforplot3<-data.frame(mean4)


#write.csv(PHforplot3,'C:/Users/r31j968/OneDrive - Montana State University - Bozeman/Documents/R analysis/PHforplot3.csv', row.names = TRUE)

emmip(m7,BL~Stress, CIs=TRUE)
```


Interaction plots


```{r}

interaction.plot(x.factor = vida$`Stress`, trace.factor = vida$BL, response = vida$`PlantHeight`, col = rainbow(5), lwd = 5, fun = function(x) mean(x, na.rm = TRUE), xlab="heat stress", ylab="plant height")

interaction.plot(x.factor = as.factor(vida$Chamber), trace.factor = vida$BL, response = vida$`PlantHeight`, col = rainbow(5), lwd = 5, fun = function(x) mean(x, na.rm = TRUE), xlab="chamber", ylab="plant height")
```


```{r}

interaction.plot(x.factor = hiline$`Stress`, trace.factor = hiline$BL, response = hiline$`PlantHeight`, col = rainbow(5), lwd = 5, fun = function(x) mean(x, na.rm = TRUE), xlab="heat stress", ylab="plant height")
```

```{r}

interaction.plot(x.factor = mth$`Stress`, trace.factor = mth$BL, response = mth$`PlantHeight`, col = rainbow(5), lwd = 5, fun = function(x) mean(x, na.rm = TRUE), xlab="heat stress", ylab="plant height")

```



Spike length - vida

```{r}
mwb3<-read_excel("combined reps.xlsx", sheet=3)

mwb3$Line<-factor(mwb3$Line)
mwb3$BL<-factor(mwb3$BL)
mwb3$HeatStress<-factor(mwb3$HeatStress)
mwb3$Rep<-factor(mwb3$Rep)
```


```{r, fig.width=8}
pirateplot(SpikeLength ~ Line + HeatStress+Rep, data=mwb3,inf.method="ci")

pirateplot(SpikeLength ~ BL+ Line + HeatStress , data=mwb3)

pirateplot(SpikeLength ~ BL+ HeatStress+Rep , data=mwb3,inf.method="ci")
```

```{r}
rep1<-read_excel("harvesting rep 1.xlsx", sheet=3)
rep2<-read_excel("harvesting rep 2.xlsx", sheet=2)
rep3<-read_excel("harvesting rep 3.xlsx", sheet=2)

```



```{r}
SL1 <- aggregate.data.frame(rep1$SpikeLength, by = list(rep1$Rep, rep1$Line,rep1$BL,rep1$Chamber,rep1$HeatStress, rep1$Plant,rep1$Spike),FUN=mean, na.rm=T)
SL2 <- aggregate(rep2$SpikeLength, by = list(rep2$Rep, rep2$Line,rep2$BL,rep2$Chamber,rep2$HeatStress, rep2$Plant,rep2$Spike), FUN=mean, na.rm=T)
SL3 <- aggregate(rep3$SpikeLength, by = list(rep3$Rep, rep3$Line,rep3$BL,rep3$Chamber,rep3$HeatStress, rep3$Plant,rep3$Spike), FUN = mean, na.rm=T)

```

```{r}

SpikeLength1<-data.frame(SL1)
SpikeLength2<-data.frame(SL2)
SpikeLength3<-data.frame(SL3)



newdata8<-rbind(SpikeLength1,SpikeLength2, SpikeLength3)

```

```{r}
colnames(newdata8)
names(newdata8)<- c("Rep","Line","BL","Chamber","Stress","Plant","Spike","SpikeLength")
```

```{r}
pirateplot(SpikeLength ~ Line + Stress, inf.method = "ci", cex.names = 0.8, ylab = "Mean Spike Length (cm)", data=newdata8)
```


```{r}
write.csv(SpikeLength1,'C:/Users/kotha/Desktop/R analysis/MWB/SpikeLength1.csv', row.names = TRUE)
write.csv(SpikeLength2,'C:/Users/kotha/Desktop/R analysis/MWB/SpikeLength2.csv', row.names = TRUE)
write.csv(SpikeLength3,'C:/Users/kotha/Desktop/R analysis/MWB/SpikeLength3.csv', row.names = TRUE)
```

```{r}
sl1<-read.csv("SpikeLength1.csv")
sl2<-read.csv("SpikeLength2.csv")
sl3<-read.csv("SpikeLength3.csv")

spikelength<-rbind(sl1,sl2,sl3)

write.csv(spikelength,'C:/Users/kotha/Desktop/R analysis/MWB/SpikeLength.csv', row.names = TRUE)
```


```{r}
newdata8<-read.csv("SpikeLength.csv")
```

```{r}
colnames(newdata8)
names(newdata8)<- c("Rep","Line","BL","Chamber","Stress","Plant","Spike","SpikeLength")
```


```{r}
vidaSL<-newdata8[newdata8$Line == "Vida",]
nd<-vidaSL
controlv2 <- newdata8[newdata8$Line == "Vida"& newdata8$BL == "C",]
seedv2 <- newdata8[newdata8$Line == "Vida"& newdata8$BL == "S",]
newdata7<-rbind(controlv2,seedv2)
```


```{r}
pirateplot(SpikeLength ~ BL+ Stress , data=nd,inf.method="ci", ylab="Mean Spike Length (cm)")
```

```{r}
m18<-lmer(SpikeLength ~ Stress + BL+(1|Rep)+(1|Chamber), data=nd)
Anova(m18, test.statistic = "F")
summary(m18)
```

```{r, fig.width=11}
intplotarray(SpikeLength~BL*HeatStress, data=nd)

```

```{r}
d<-emmeans(m18, c("BL", "HeatStress"))
emmip(m18,BL~HeatStress, CIs=TRUE)
emmip(m18,BL~HeatStress)
plot(d, comparison=T)
```

```{r}
nd$treat<-with(nd, interaction(BL,Stress))

model2<-lmer(SpikeLength~treat+(1|Rep)+(1|Chamber), data=nd)

trt2<-glht(model2,linfct=mcp(treat="Tukey"))
summary(trt2)
confint(trt2)
```

```{r}
m9<-lmer(SpikeLength ~ HeatStress + BL+(1|Rep)+(1|Chamber), data=newdata7)
Anova(m9, test.statistic = "F")
summary(m9)
```

```{r}
mean2<-emmeans(m9,c("BL","HeatStress"))
SHforplot<-data.frame(mean2)


#write.csv(SHforplot,'C:/Users/r31j968/OneDrive - Montana State University - Bozeman/Documents/R analysis/SHforplot.csv', row.names = TRUE)
```


```{r}
emmip(m9,BL~HeatStress, CIs=TRUE)
```




```{r, fig.width=11}
intplotarray(SpikeLength~BL*HeatStress, data=newdata7)

```



```{r}
m10<-lmer(SpikeLength ~ HeatStress * BL+(1|Rep)+(1|Chamber), data=newdata7)
Anova(m10, test.statistic = "F")
summary(m10)
```
No interaction. Use additive model. 




```{r}
hilSL<-newdata8[newdata8$Line == "Hiline",]
nd4<-hilSL
mthSL<-newdata8[newdata8$Line == "MTH",]
nd5<-mthSL
```


```{r}
pirateplot(SpikeLength ~ BL+ Stress , data=nd4,inf.method="ci", ylab="Mean Spike Length (cm)")
```


```{r}
pirateplot(SpikeLength ~ BL+ Stress , data=nd5,inf.method="ci", ylab="Mean Spike Length (cm)")
```


```{r, fig.width=11}
intplotarray(SpikeLength~BL*HeatStress, data=nd4)
intplotarray(SpikeLength~BL*HeatStress, data=nd5)

```

```{r}
m25<-lmer(SpikeLength ~ Stress * BL+(1|Rep)+(1|Chamber), data=nd4)
Anova(m25, test.statistic = "F")
summary(m25)
```


```{r}
e<-emmeans(m25, c("BL", "HeatStress"))
plot(e, comparison=T)
```

```{r}
nd4$treat<-with(nd4, interaction(BL,Stress))

model3<-lmer(SpikeLength~treat+(1|Rep)+(1|Chamber), data=nd4)

trt3<-glht(model3,linfct=mcp(treat="Tukey"))
summary(trt3)
confint(trt3)
```

```{r}
m26<-lmer(SpikeLength ~ Stress * BL+(1|Rep)+(1|Chamber), data=nd5)
Anova(m26, test.statistic = "F")
summary(m26)
```

```{r}
m<-lmer(SpikeLength ~ Stress + BL+(1|Rep)+(1|Chamber), data=nd5)
Anova(m, test.statistic = "F")
summary(m)
```

```{r}
#f<-emmeans(m26, c("BL", "HeatStress"))
#plot(f, comparison=T)
```

```{r}
nd5$treat<-with(nd5, interaction(BL,Stress))

model4<-lmer(SpikeLength~treat+(1|Rep)+(1|Chamber), data=nd5)

trt4<-glht(model4,linfct=mcp(treat="Tukey"))
summary(trt4)
```



Grain no per spike 

```{r}
rep2<-read_excel("harvesting rep 2.xlsx", sheet=2)
rep1<-read_excel("harvesting rep 1.xlsx", sheet=3)
rep3<-read_excel("harvesting rep 3.xlsx", sheet=2)

```



```{r}
gN1 <- aggregate(rep1$GrainNo., by = list(rep1$Rep, rep1$Line,rep1$BL,rep1$Chamber,rep1$HeatStress, rep1$Plant,rep1$Spike), FUN = sum)
gN2 <- aggregate(rep2$GrainNo., by = list(rep2$Rep, rep2$Line,rep2$BL,rep2$Chamber,rep2$HeatStress, rep2$Plant,rep2$Spike), FUN=sum)
gN3 <- aggregate(rep3$GrainNo., by = list(rep3$Rep, rep3$Line,rep3$BL,rep3$Chamber,rep3$HeatStress, rep3$Plant,rep3$Spike), FUN = sum)

```


###do not run, only for making data sheets (for 1000 grain weight)
```{r}
g1 <- aggregate(rep1$GrainNo., by = list(rep1$Rep, rep1$Line,rep1$BL,rep1$Chamber,rep1$HeatStress, rep1$Plant), FUN = sum)
g2 <- aggregate(rep2$GrainNo., by = list(rep2$Rep, rep2$Line,rep2$BL,rep2$Chamber,rep2$HeatStress, rep2$Plant), FUN=sum)
g3 <- aggregate(rep3$GrainNo., by = list(rep3$Rep, rep3$Line,rep3$BL,rep3$Chamber,rep3$HeatStress, rep3$Plant), FUN = sum)

grain1<-data.frame(g1)
grain2<-data.frame(g2)
grain3<-data.frame(g3)

thousand<-rbind(g1,g2,g3)

write.csv(thousand,'C:/Users/kotha/Desktop/R analysis/MWB/thousand.csv', row.names = TRUE)
```
write.csv(grain1,'C:/Users/r31j968/OneDrive - Montana State University - Bozeman/Documents/R analysis/grain1.csv', row.names = TRUE)
write.csv(grain2,'C:/Users/r31j968/OneDrive - Montana State University - Bozeman/Documents/R analysis/grain2.csv', row.names = TRUE)
write.csv(grain3,'C:/Users/r31j968/OneDrive - Montana State University - Bozeman/Documents/R analysis/grain3.csv', row.names = TRUE)




```{r}

grainNo1<-data.frame(gN1)
grainNo2<-data.frame(gN2)
grainNo3<-data.frame(gN3)



newdata15<-rbind(grainNo1,grainNo2, grainNo3)

```


write.csv(grainNo1,'C:/Users/kotha/Desktop/R analysis/MWB/grainNo1.csv', row.names = TRUE)
write.csv(grainNo2,'C:/Users/kotha/Desktop/R analysis/MWB/grainNo2.csv', row.names = TRUE)
write.csv(grainNo3,'C:/Users/kotha/Desktop/R analysis/MWB/grainNo3.csv', row.names = TRUE)

```{r}
write.csv(newdata15,'C:/Users/kotha/Desktop/R analysis/MWB/grainNo.csv', row.names = TRUE)
```


```{r}
names(newdata15)[names(newdata15) == "Group.1"] <- "Rep"
names(newdata15)[names(newdata15) == "Group.2"] <- "Line"
names(newdata15)[names(newdata15) == "Group.3"] <- "BL"
names(newdata15)[names(newdata15) == "Group.4"] <- "Chamber"
names(newdata15)[names(newdata15) == "Group.5"] <- "HS"
names(newdata15)[names(newdata15) == "Group.6"] <- "Plant"
names(newdata15)[names(newdata15) == "Group.7"] <- "Spike"
names(newdata15)[names(newdata15) == "x"] <- "GrainNo"
```

```{r}
newdata15<-read.csv("grainNo.csv")
```


```{r}
newdata15$Line<-factor(newdata15$Line)
newdata15$BL<-factor(newdata15$BL)
newdata15$HS<-factor(newdata15$HS)
newdata15$Rep<-factor(newdata15$Rep)
```


```{r}
pirateplot(GrainNo ~ Line+ HS , data=newdata15,inf.method="ci", ylab="Grain number per spike")
```


```{r}
vidaGN <- newdata15[newdata15$Line == "Vida",]
hilGN <- newdata15[newdata15$Line == "Hiline",]
mthGN <- newdata15[newdata15$Line == "MTH",]
nd6<-vidaGN
nd7<-hilGN
nd8<-mthGN
```


```{r}
pirateplot(GrainNo ~ BL+ HS , data=nd6,inf.method="ci", ylab="Grain number per spike")
```


```{r}
pirateplot(GrainNo ~ BL+ HS , data=nd7,inf.method="ci", ylab="Grain number per spike")
```


```{r}
pirateplot(GrainNo ~ BL+ HS , data=nd8,inf.method="ci", ylab="Grain number per spike")
```


```{r}
m13<-lmer(GrainNo ~ HS * BL+(1|Rep)+(1|Chamber), data=newdata15)
Anova(m13, test.statistic = "F")
summary(m13)
```

```{r, fig.width=11}
intplotarray(GrainNo ~ HS * BL, data=newdata15)
```

```{r}
m27<-lmer(GrainNo ~ HS * BL+(1|Rep)+(1|Chamber), data=nd6)
Anova(m27, test.statistic = "F")
summary(m27)
```

```{r}
g<-emmeans(m27, c("BL", "HS"))
plot(g, comparison=T)
```

```{r}
nd6$treat<-with(nd6, interaction(BL,HS))

model5<-lmer(GrainNo~treat+(1|Rep)+(1|Chamber), data=nd6)

trt5<-glht(model5,linfct=mcp(treat="Tukey"))
summary(trt5)
confint(trt5)
```

```{r}
m28<-lmer(GrainNo ~ HS * BL+(1|Rep)+(1|Chamber), data=nd7)
Anova(m28, test.statistic = "F")
summary(m28)
```

```{r}
h<-emmeans(m28, c("BL", "HS"))
plot(h, comparison=T)
```


```{r}
nd7$treat<-with(nd7, interaction(BL,HS))

model6<-lmer(GrainNo~treat+(1|Rep)+(1|Chamber), data=nd7)

trt6<-glht(model6,linfct=mcp(treat="Tukey"))
summary(trt6)
confint(trt6)
```

```{r}
m29<-lmer(GrainNo ~ HS + BL+(1|Rep)+(1|Chamber), data=nd8)
Anova(m29, test.statistic = "F")
summary(m29)
```

```{r}
i<-emmeans(m29, c("BL", "HS"))
plot(i, comparison=T)
```

```{r}
nd8$treat<-with(nd8, interaction(BL,HS))

model7<-lmer(GrainNo~treat+(1|Rep)+(1|Chamber), data=nd8)

trt7<-glht(model7,linfct=mcp(treat="Tukey"))
summary(trt7)
```

```{r, fig.width=11}
intplotarray(GrainNo ~ HS * BL, data=nd6)
intplotarray(GrainNo ~ HS * BL, data=nd7)
intplotarray(GrainNo ~ HS * BL, data=nd8)

```

```{r}
vida_C <- newdata15[newdata15$Line == "Vida"& newdata15$BL == "C",]
vida_S <- newdata15[newdata15$Line == "Vida"& newdata15$BL == "S",]
newdata9<-rbind(vida_C,vida_S)
```

```{r}
m14<-lmer(GrainNo ~ HS * BL+(1|Rep)+(1|Chamber), data=newdata9)
Anova(m14, test.statistic = "F")
summary(m14)
```

```{r, fig.width=11}
intplotarray(GrainNo ~ HS * BL, data=newdata9)
```

```{r}
mean5<-emmeans(m14,c("BL","HS"))

emmip(m14,BL~HS, CIs=TRUE)
```

```{r}
emmip(m14,BL~HS)

```




```{r, fig.width=11}
intplotarray(GrainNo~BL*HS, data=newdata9)
```





```{r}
thGW<-read_excel("1000 grain weight.xlsx", sheet=1)
```

```{r}
pirateplot(tGW~Line+HS, data=thGW, inf.method = "ci", ylab="1000 grain weight (g)")
```


```{r}
m23<-lmer(tGW~BL*HS+(1|Rep), data=thGW)
Anova(m23, test.statistic = "F")
summary(m23)
```

```{r}
m24<-lmer(tGW~BL+HS+(1|Rep), data=thGW)
Anova(m24, test.statistic = "F")
summary(m24)
```

```{r, fig.width=11}
intplotarray( tGW~BL*HS, data=thGW)
```

```{r}
pirateplot(tGW~BL+HS, data=thGW, inf.method = "ci")
```

```{r}
boxplot(tGW~BL+HS, data=thGW)

```

```{r}
vidaGW <- thGW[thGW$Line == "Vida",]
hilGW <- thGW[thGW$Line == "Hiline",]
mthGW <- thGW[thGW$Line == "MTH",]
nd1<-vidaGW
nd2<-hilGW
nd3<-mthGW
```


```{r}
pirateplot(tGW~BL+HS, data=nd1, inf.method = "ci", ylab="1000 grain weight (g)")
pirateplot(tGW~BL+HS, data=nd2, inf.method = "ci",ylab="1000 grain weight (g)")
pirateplot(tGW~BL+HS, data=nd3, inf.method = "ci",ylab="1000 grain weight (g)")

```



```{r, fig.width=11}
intplotarray( tGW~BL*HS, data=nd1)
intplotarray( tGW~BL*HS, data=nd2)
intplotarray( tGW~BL*HS, data=nd3)
```

```{r}
m30<-lmer(tGW~BL+HS+(1|Rep)+(1|Chamber), data=nd1)
Anova(m30, test.statistic = "F")
summary(m30)
```

```{r}
j<-emmeans(m30, c("BL", "HS"))
j
cld(j, Letters = "abcdef")
```

```{r}
trt8<-glht(m30, linfct=mcp("BL"="Tukey","HS"="Tukey"))
summary(trt8)
confint(trt8)
```


```{r}
nd1$treat<-with(nd1, interaction(BL,HS))

model8<-lmer(tGW~treat+(1|Rep), data=nd1)

trt8<-glht(model8,linfct=mcp(treat="Tukey"))
summary(trt8)
```

```{r}
m31<-lmer(tGW~BL*HS+(1|Rep), data=nd2)
Anova(m31, test.statistic = "F")
summary(m31)
```

```{r}
k<-emmeans(m31, c("BL", "HS"))
plot(k, comparison=T)
```

```{r}
nd2$treat<-with(nd2, interaction(BL,HS))

model9<-lmer(tGW~treat+(1|Rep), data=nd2)

trt9<-glht(model9,linfct=mcp(treat="Tukey"))
summary(trt9)
```

```{r}
m32<-lmer(tGW~BL+HS+(1|Rep), data=nd3)
Anova(m32, test.statistic = "F")
summary(m32)
```

```{r}
l<-emmeans(m32, c("BL", "HS"))
plot(l, comparison=T)
```

```{r}
nd3$treat<-with(nd3, interaction(BL,HS))

model10<-lmer(tGW~treat+(1|Rep), data=nd3)

trt10<-glht(model10,linfct=mcp(treat="Tukey"))
summary(trt10)
```



write.xlsx(x, file, sheetName = "Sheet1", 
  col.names = TRUE, row.names = TRUE, append = FALSE)
write.xlsx2(x, file, sheetName = "Sheet1",
  col.names = TRUE, row.names = TRUE, append = FALSE)
  
x: a data.frame to be written into the workbook
file: the path to the output file
sheetName: a character string to use for the sheet name.
col.names, row.names: a logical value specifying whether the column names/row names of x are to be written to the file
append: a logical value indicating if x should be appended to an existing file.
